---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# daqr

<!-- badges: start -->
<!-- badges: end -->

`daqr` provides functions to work with Data AcQuisition (DAQ) files generated by minisim driving simulator. With `daqr`, you can convert a `daq` file to `hdf5` type, and get useful driving variables directly in R. `daqr` uses [undaqTools]() python package by Roger Lew behind the scenes.  

## Installation

You can install the development version of daqr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("durraniu/daqr")
```

## Getting ready to use `daqr`

You need to have python 2.7 and a few packages installed to use `daqr`. You can get python and packages in one of the two ways discussed below.  

### Python already installed

If you already have python 2.7 installed, then make sure that you have the following packages or install them:  

* scipy  
* numpy  
* matplotlib  
* h5py  
* nose  
* sphinx 
* numpydoc  
* undaqTools  

Then you can use `reticulate` to specify this installation of python to start using `daqr`:  

```{python, eval=FALSE}
reticulate::use_python("path/to/python.exe")
```

### Python not installed

To start from scratch, first install python, create a virtual environment, and install dependencies using `reticulate`:  

```{r, eval=FALSE}
library(reticulate)

path_to_python <- install_python(version="2.7.18")
virtualenv_create("r-reticulate", python = path_to_python)


py_install(packages = c("scipy", "numpy", "matplotlib", "h5py",
                        "nose", "sphinx", "numpydoc", "undaqTools"),
           python_version = "2.7.18",
           envname = "r-reticulate")
```


## Using `daqr`

### Converting a `daq` file to `hdf5`:  

The function `read_daq_and_save_to_hdf5` will read the `daq` file and save it to `hdf5` format in the same location using the same file name.

```{r example1, eval=FALSE}
library(daqr)
library(reticulate)

## Specify the environment to use
use_virtualenv("r-reticulate")

read_daq_and_save_to_hdf5("path/to/daq/file.daq")
```



### Getting driver data

You can get several variables from driving data using the function `read_driver_data`. It takes two arguments for `file_name` and `metric`. The `file_name` parameter can be a `daq` file or a `hdf5` file. The units of variables in the resulting dataframe depends on `metric`. If `TRUE`, then the units will be metric, if `FALSE`, the units will be english.  

```{r example2, eval=FALSE}
library(daqr)
library(reticulate)

## Specify the environment to use
use_virtualenv("r-reticulate")

# Get driving data from daq file
read_driver_data("path/to/daq/file.daq")

# Get driving data from previously saved hdf5 file
read_driver_data("path/to/hdf5/file.hdf5")
```

